---
title: "index file"
author: "Raksha Bohra"
date: "11/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introductory Paragraph
The World Happiness Index measures happiness based on respondent's ratings of their own lives. The report offers a way to measure people's quality of life and the effectiveness of the governments beyond gross domestic product and other economic indicators. By focusing on national well being, a country can take a more wholistic approach to improving their populace's lives. The United Nations conducts the survey based on a ladder system by asking respondents to rate the best possible life at 10 and the worst possible life being a 0. Respondents from 155 countries are then asked to rate their own current lives on that 0 to 10 scale. 

```{r, eval = TRUE}
source("scripts/summary_info.R")
dataset <- read.csv(
  file = "data/world-happiness/2017.csv",
  stringsAsFactors = FALSE)
summary_list <- get_summary_info(dataset)
```
## Summary Information

The World Happiness Index surveyed `r summary_list$num_row` countries. The happiest country in the world in 2017 was `r summary_list$happiest_country` with a score of `r summary_list$highest_happiness_score`. The unhappiest country in the world was `r summary_list$unhappiest_country` with a score of `r summary_list$lowest_happiness_score` 

##Including Table
```{r, eval = TRUE}
library(knitr)
source("scripts/table_script.R")
table <- aggregate_table(dataset)
kable(table)
```




We wanted to investigate the correlations between GDP per capita and Happiness score. As a result, we grouped countries with similiar GDP per capita together and calculated the average Happiness score for all countries within each group. The results are then displayed in the table above.


## Including Plots
```{r, echo = FALSE, eval= TRUE}
source("scripts/happy_analysis.R")
happy_free_plot <- get_happiness_analysis(dataset)

```
`r happy_free_plot`

This chart visualizes what the freedom score of the top ten happiest countries. Freedom score is calculated by the Cato Institute using 79 distinct indicators of personal and economic freedom. The graph shows that the happiest countries share a similiar degree of freedom that can show correlation between the freedom and happiness scores. 

```{r, echo = FALSE, eval = TRUE}
library(plotly)
source("scripts/Happiness_VS_Health.R")
graph_2017 <- get_happiness_vs_health(dataset)

graph_2017
```


This chart was intended to show the relationship between health and happiness score in 2017. We found from the line chart that there is a positive relationship between health, measured by life expectancy,  and happiness, that is— the higher the life expectancy, the more happy they are. 

